### 2016-04-19 Manuscript/SW_early_life_telomeres.Rmd
DSR edits

Early-life RTL was not related to survival to adulthood (estimate = `r round2(summary(glmer(SurvivedNext~RTL+(1|FieldPeriodID),data=subset(juv13,Agemonths ==1),family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glmer(SurvivedNext~RTL+Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv13,family = 'binomial'))$coefficients[2,4])`), with no interaction effect between RTL and juvenile age (estimate = `r round2(summary(glmer(SurvivedNext~RTL*Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv13,family = 'binomial'))$coefficients[4,1])`; P = `r round2(summary(glmer(SurvivedNext~RTL*Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv13,family = 'binomial'))$coefficients[4,4])`). To test whether cohort-level effects on RTL influenced survival we calculated cohort-level RTL (i.e. the median RTL for each cohort) and added this term to a GLMM, and found that cohort-level RTL was not related to survival to adulthood (estimate = `r round2(summary(glmer(SurvivedNext~cohortTL+RTL+Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv13,family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glmer(SurvivedNext~cohortTL+RTL+Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv13,family = 'binomial'))$coefficients[2,4])`). Using the longitudinal data, we found that $\Delta$RTL had no effect on survival to the year after the second sampling event (estimate = `r round2(summary(glm(SurvivedNext2~Loss+Agemonths,data = subset(Loss,FieldPeriodID<2013),family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glm(SurvivedNext2~Loss+Agemonths,data=subset(Loss,LayYear<2013),family = 'binomial'))$coefficients[2,4])`).

>>>>

Early-life RTL was not related to survival to adulthood (estimate = `r round2(summary(glmer(SurvivedNext~RTL+(1|FieldPeriodID),data=subset(juv13,Agemonths ==1),family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glmer(SurvivedNext~RTL+Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv13,family = 'binomial'))$coefficients[2,4])`), with no interaction effect between RTL and juvenile age (estimate = `r round2(summary(glmer(SurvivedNext~RTL*Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv13,family = 'binomial'))$coefficients[4,1])`; P = `r round2(summary(glmer(SurvivedNext~RTL*Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv13,family = 'binomial'))$coefficients[4,4])`). To test whether cohort-level effects on RTL influenced survival we calculated cohort-level RTL (i.e. the median RTL for each cohort) and added this term to a GLMM, and found that cohort-level RTL was not related to survival to adulthood (estimate = `r round2(summary(glmer(SurvivedNext~cohortTL+RTL+Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv13,family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glmer(SurvivedNext~cohortTL+RTL+Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv13,family = 'binomial'))$coefficients[2,4])`). Using the longitudinal data, we found that $\Delta$RTL had no effect on survival to the year after the second sampling event (estimate = `r round2(summary(glm(SurvivedNext2~Loss+Agemonths,data = subset(Loss,LayYear<2013),family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glm(SurvivedNext2~Loss+Agemonths,data=subset(Loss,LayYear<2013),family = 'binomial'))$coefficients[2,4])`).
